Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Split up introduction to approaches
Briefly go over Kruger method again in introduction to approaches

We take two different approaches to rendering intersecting volumes using boolean
operations.  The boolean operations involved are AND and XOR.  AND takes the
intersection of two shapes, while XOR, meaning exclusive OR, takes everything
but the intersection.

>>>>

We take two different approaches to rendering intersecting volumes using boolean
operations.

The boolean operations involved are AND and XOR.  AND takes the intersection of
two shapes, while XOR, meaning exclusive OR, takes everything but the
intersection.

Both approaches are based on the volume rendering method in \cite{Kruger03}, as
previously mentioned.  To render part of a volume, they first render the texture
coordinates of the back faces of that part to a texture.  Then the front faces
of that part are rendered with a shader that uses the previously-stored texture
coordinates to form a ray through the volume.  The ray then samples the volume
at regular intervals.
